``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)

### 2022-12-23 paper/04--otherLinearization.tex
captions, ref, etc
delete 99 qote

 \begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

		\end{subfigure}
	}
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

	\scalebox{0.75}{
		\begin{subfigure}{4.5cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

\begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{7cm}
		 	\centering
			\caption{Resulting method ordering has a cycle}
			\label{fig:CycleBreaking1}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{6cm}
		 %	\centering
			\caption{Delete any random ordering to break it}
			\label{fig:CycleBreaking2}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}
		\end{subfigure}
	}
	\caption{Example of Cycle-Breaking the Desired Additional Orderings\label{fig:CycleBreaking}\Psays{Ying, captions come in figures always below the graphics. Can you fix this? The captions are also not self-explanatory. E.g. in (a) you mention 'resulting', but it's completely unclear what you are referring to. Caption (b) is also not self-explanatory.}}
\end{figure}

>>>>

 \begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{4cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

		\end{subfigure}
	}
	\scalebox{0.75}{
		\begin{subfigure}{4cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

	\scalebox{0.75}{
		\begin{subfigure}{4cm}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

\begin{figure}[h]
	\scalebox{0.75}{
		\begin{subfigure}{7cm}
		 %	\centering
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}
			\caption{A method that has the orderings from Figure~\ref{fig:OrderingRules} has a cycle}
			\label{fig:CycleBreaking1}
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{6cm}
		 %	\centering
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

@@

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}
			\caption{Delete any random ordering to break the cycle.}
			\label{fig:CycleBreaking2}
		\end{subfigure}
	}
	\caption{Example of Cycle-Breaking Until the Method No Longer Has Any Cycles \label{fig:CycleBreaking}\Psays{Ying, captions come in figures always below the graphics. Can you fix this? The captions are also not self-explanatory. E.g. in (a) you mention 'resulting', but it's completely unclear what you are referring to. Caption (b) is also not self-explanatory.}}
\end{figure}
